word lists

### 2021-05-26 analysis/word_lists.Rmd
add annotated word lists

>>>>

# Selected words from combined lists

For selections criteria see: `../docs/conding.md`.

```{r}
file.list <- list.files(path = "../data/annotated_word_lists/", pattern='*.xlsx', full.names = T)

ad <- lapply(file.list, read_xlsx)%>%bind_rows()%>%
  arrange(aoa_german_comb)%>%
  filter(select == "x")%>%
  select(1:7)

# add word type inforamtion

wt <- read_xlsx("../data/annotated_word_lists/word_list_collection_all.xlsx", skip = 1)%>%
  slice(-1)%>%
  pivot_longer(names_to = "word_type", values_to = "word", cols = 1:30)%>%
  mutate(word_type = gsub("\\..*","",word_type))%>%
  filter(!is.na(word))%>%
  mutate(word_type = recode(word_type, adj = "adjective", nouns = "noun", verbs = "verb"))%>%
  rename(german = word)%>%
  select(german, word_type)

fw <- ad%>%left_join(wt)%>%
  mutate(word_type = ifelse(german == "bürste", "noun", word_type),
         word_type = ifelse(german == "magnetisch", "adjective", word_type),
         word_type = ifelse(german == "gerechtigkeit", "noun", word_type))

write_csv(fw, file = "../data/word_list.csv")

```
## Distribution of selected words by age and word type

```{r}
fw%>%
  ggplot(aes(x = aoa_german_comb, fill = word_type))+
  geom_histogram(alpha = .5, col = "black", binwidth = 0.25, position = "identity")+
  theme_minimal()+
  xlim(1,11)+
  facet_grid(~word_type)+
  scale_fill_viridis_d()
```
